\LaTeXe\ guide for the Journal of Functional Programming

### 2019-04-28 papers/jfp/3-abstractions.tex
Make sure S3 doesn't overflow the margins

\begin{figure}
% \vspace{-1mm}
\begin{minted}[fontsize=\small]{haskell}
-- An abstract store containing a key/value map and persistent build information
data Store i k v -- i = info, k = key, v = value
initialise :: i -> (k -> v) -> Store i k v
getInfo    :: Store i k v -> i
putInfo    :: i -> Store i k v -> Store i k v
getValue   :: k -> Store i k v -> v
putValue   :: Eq k => k -> v -> Store i k v -> Store i k v
\end{minted}
% \vspace{-1mm}
\begin{minted}[fontsize=\small]{haskell}
data Hash v -- a compact summary of a value with a fast equality check
hash    :: Hashable v => v -> Hash v
getHash :: Hashable v => k -> Store i k v -> Hash v
\end{minted}
% \vspace{-1mm}
\begin{minted}[fontsize=\small]{haskell}
-- Build tasks (see §3.2)
newtype Task  c k v = Task { run :: @\std{forall}@ f. c f => (k -> f v) -> f v }
type    Tasks c k v = k -> Maybe (Task c k v)
\end{minted}
% \vspace{-1mm}
\begin{minted}[fontsize=\small]{haskell}
-- Build system (see §3.3)
type Build c i k v = Tasks c k v -> k -> Store i k v -> Store i k v
\end{minted}
% \vspace{-1mm}
\begin{minted}[fontsize=\small]{haskell}
-- Build system components: a scheduler (see §4) and a rebuilder (see §5)
type Scheduler c i ir k v = Rebuilder c ir k v -> Build c i k v
type Rebuilder c   ir k v = k -> v -> Task c k v -> Task (MonadState ir) k v
\end{minted}
% \vspace{-3.5mm}
\caption{Type signatures of key build systems abstractions.}\label{fig-types}
% \vspace{-4.5mm}
\end{figure}

@@

\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
ackermann :: Tasks Monad (Integer, Integer) Integer
ackermann (m, n)
  | m < 0 || n < 0 = Nothing
  | m == 0    = Just $ Task $ const $ pure (n + 1)
  | n == 0    = Just $ Task $ \fetch -> fetch (m - 1, 1)
  | otherwise = Just $ Task $ \fetch -> do index <- fetch (m, n - 1)
                                           fetch (m - 1, index)
\end{minted}
\vspace{1mm}

@@

cloudAckermann :: Tasks (MonadState Cache) (Integer, Integer) Integer
cloudAckermann (m, n)
    | m < 0 || n < 0 = Nothing
    | m == 0    = Just $ Task $ const $ pure (n + 1)
    | n == 0    = Just $ Task $ \fetch -> fetch (m - 1, 1)
    | otherwise = Just $ Task $ \fetch -> do
        cache <- get
        case Map.lookup (m, n) cache of
            Nothing -> do index <- fetch (m, n - 1)
                          value <- fetch (m - 1, index)
                          modify (Map.insert (m, n) value)
                          return value
            Just value -> return value
\end{minted}
\vspace{1mm}

>>>>

\begin{figure}
% \vspace{-1mm}
\begin{minted}[fontsize=\small]{haskell}
-- Abstract store containing a key/value map and persistent build information
data Store i k v -- i = info, k = key, v = value
initialise :: i -> (k -> v) -> Store i k v
getInfo    :: Store i k v -> i
putInfo    :: i -> Store i k v -> Store i k v
getValue   :: k -> Store i k v -> v
putValue   :: Eq k => k -> v -> Store i k v -> Store i k v
\end{minted}
% \vspace{-1mm}
\begin{minted}[fontsize=\small]{haskell}
data Hash v -- a compact summary of a value with a fast equality check
hash    :: Hashable v => v -> Hash v
getHash :: Hashable v => k -> Store i k v -> Hash v
\end{minted}
% \vspace{-1mm}
\begin{minted}[fontsize=\small]{haskell}
-- Build tasks (see §3.2)
newtype Task  c k v = Task { run :: @\std{forall}@ f. c f => (k -> f v) -> f v }
type    Tasks c k v = k -> Maybe (Task c k v)
\end{minted}
% \vspace{-1mm}
\begin{minted}[fontsize=\small]{haskell}
-- Build system (see §3.3)
type Build c i k v = Tasks c k v -> k -> Store i k v -> Store i k v
\end{minted}
% \vspace{-1mm}
\begin{minted}[fontsize=\small]{haskell}
-- Build system components: a scheduler (see §4) and a rebuilder (see §5)
type Scheduler c i ir k v = Rebuilder c ir k v -> Build c i k v
type Rebuilder c   ir k v = k -> v -> Task c k v -> Task (MonadState ir) k v
\end{minted}
% \vspace{-3.5mm}
\caption{Type signatures of key build systems abstractions.}\label{fig-types}
% \vspace{-4.5mm}
\end{figure}

@@

\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
ackermann :: Tasks Monad (Integer, Integer) Integer
ackermann (m, n)
  | m < 0 || n < 0 = Nothing
  | m == 0    = Just $ Task $ const $ pure (n+1)
  | n == 0    = Just $ Task $ \fetch -> fetch (m-1, 1)
  | otherwise = Just $ Task $ \fetch -> do index <- fetch (m, n-1)
                                           fetch (m-1, index)
\end{minted}
\vspace{1mm}

@@

cloudAck :: Tasks (MonadState Cache) (Integer, Integer) Integer
cloudAck (m, n)
    | m < 0 || n < 0 = Nothing
    | m == 0    = Just $ Task $ const $ pure (n+1)
    | n == 0    = Just $ Task $ \fetch -> fetch (m-1, 1)
    | otherwise = Just $ Task $ \fetch -> do
        cache <- get
        case Map.lookup (m, n) cache of
            Nothing -> do index <- fetch (m, n-1)
                          value <- fetch (m-1, index)
                          modify (Map.insert (m, n) value)
                          return value
            Just value -> return value
\end{minted}
\vspace{1mm}
